DSSynth: An Automated Synthesis Tool of Digital \\ Controllers for Physical Plants via MATLAB Toolbox

### 2017-06-04 ase2017/paper.tex
updated illustrative example

\usepackage{xspace,framed}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{subfigure} 
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cite}

@@

\newcommand\tool{{DSSynth Toolbox}\xspace}

@@

\begin{verbatim} synthesize(plant, intBits, fracBits, maxR, minR) \end{verbatim}

@@

To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the 
synthesis for a physical plant defined in Eq.(~\ref{equation_plant}),
which represents a UAV a quadcopter system, whose model was described by Bouabdallah {\it et al.}~\cite{bouabdallah}. The physical plant in Eq.(~\ref{equation_plant}) is represented using the transfer-function format, where ``num'' and ``den'' 
represent the numerator $A(z)$ and denominator $B(z)$, respectively.
%
\begin{equation}
\label{equation_plant}
H(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089}.
\end{equation}
%
\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> system = tf(num,den,0.002);
>> y = synthesize(system,8,8,1,-1);
>> SYNTHESIS SUCCESSFUL
>> y = (-0.9983z^2 + 0.09587z + 0.1926)/(z^2+0.5665+0.75);
\end{lstlisting}
\vspace{-0.2cm}
\caption{Synthesis of a digital controller for the physical plant defined in Eq.(~\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
\label{toolbox-usage}
\end{figure}
%
In Fig.~\ref{toolbox-usage}, the value returned in variable $y$ represents 
the synthesized stable digital controller. In order to validate and reproduce 
the stability of the digital system composed by the physical plant defined in Eq.(~\ref{equation_plant}) 
and the digital controller represented by $y$, the user can invoke the step response using the 
command \texttt{dstep}, and then observe that the plotted graph shows a stable digital system, 
as shown in Fig.~\ref{step-response}.
%
\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{step-response.eps}
  \caption{Step response for the Eq.~\eqref{equation_plant} describing a stable system.}
  \label{step-response}
\end{figure}

>>>>

\usepackage{xspace,framed}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{subfigure} 
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cite}	
\usepackage{mathtools}

@@

\newcommand\tool{{DSSynth Toolbox}\xspace}
\newcommand{\fwl}[1]{\mathcal{FWL}[#1]}

@@

\begin{center} 
\texttt{synthesize(plant, intBits, fracBits, maxR, minR)}
\end{center}

@@

To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the 
synthesis for a physical plant defined in Eq.(~\ref{equation_plant}),
which represents a UAV a quadcopter system, whose model was described by Bouabdallah {\it et al.}~\cite{bouabdallah}. The physical plant in Eq.(~\ref{equation_plant}) is represented using the transfer-function format, where ``num'' and ``den'' 
represent the numerator $A(z)$ and denominator $B(z)$, respectively.
%
\begin{equation}
\label{equation_plant}
G(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089}.
\end{equation}
%
\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> system = tf(num,den,0.002);
>> y = synthesize(system,8,8,1,-1);
>> SYNTHESIS SUCCESSFUL
>> y = 
>>  -0.9983 z^2 + 0.09587 z + 0.1926
>>  --------------------------------
>>       z^2 + 0.5665 z + 0.75
\end{lstlisting}
\vspace{-0.2cm}
\caption{Synthesis of a digital controller for the physical plant defined in Eq.(\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
\label{toolbox-usage}
\end{figure}
%
In Fig.~\ref{toolbox-usage}, the value returned in variable $y$ represents 
the synthesized stable digital controller, which could be expressed in Eq.(\ref{equation_controller}).

\begin{equation}
\label{equation_controller}
H(z)=\frac{-0.9983^{2}+0.09587z+0.1926}{z^2+0.5665z+0.75}.
\end{equation}

In addition, a digital system is stable \textit{iff} all of its poles are inside the $z$-plane unitary circle; poles must have the modulus less than one. In order to compute the poles from the digital system represented by the physical plant and the controller defined in Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), respectively, the user can use \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab} to achieve a general equation regarding the transfer-function representation. The general equation that represents the combination between Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}) is represented by Eq.~(\ref{equation_general}):
%
\begin{equation}
\small
\label{equation_general}
\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{1.069z^{4} - 1.136z^{3} + 0.4849z^{2} -0.8704z + 0.5317}.
\end{equation}

Applying the FWL effects in the $D(z)$ in order to compute the roots for stability reproduction, then if any root has modulus equal or greater than one, then the system is unstable; otherwise, it is stable. In fact, the roots computed by the function \texttt{roots} in MATLAB resulted in $-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, which means that DSSynth returned a stable digital controller.

Simulating the digital system represented by Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), in order to validate and reproduce the stability, the user can invoke the step response using the 
command \texttt{dstep}, and then observe that the plotted graph shows a stable digital system, 
as shown in Fig.~\ref{step-response}.
%
\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{step-response.eps}
  \caption{Step response for the Eq.~\eqref{equation_plant} describing a stable system.}
  \label{step-response}
\end{figure}
